quickmapr
=========

[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/0.1.0/active.svg)](http://www.repostatus.org/#active)  [![travis_status](https://travis-ci.org/jhollist/quickmapr.svg)](https://travis-ci.org/jhollist/quickmapr)  [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/jhollist/quickmapr?branch=master)](https://ci.appveyor.com/project/jhollist/quickmapr)

There are many packages that already exist or are in active development that support the visualization of spatial data in R.  However, there seems to be a gap for those that need to quickly view, compare, and explore the results of a given spatial analysis. The current thinking for `quickmapr` is to allow for quick visualization of `sp` and `raster` objects. 

Planned functionality for the first release is for easy mapping of multiple layers, simple zooming, panning, and labelling.  These tools are intended for use within an active spatial analysis workflow and not for production quality maps.

`quickmapr` is built as a series of wrapper functions for the default `sp` plotting functions and currently utilizes either the `zoom` packages for zooming and panning or simply re-plots the maps with new x and y limits. Currently there are 8 commands planned.  As the idea behind this is to quickly map data, an emphasis was given to brevity of function names.  The commands are:

- `qmap()`: creates the map
- `zi()`: zooms in
- `zo()`: zooms out
- `ze()`: zoom in to an extent
- `p()`: pans
- `l()`: adds labels
- `i()`: identify features
- `f()`: returns to extent of originally created map

A function for pulling in basemaps (aerials or topo-quads) from the USGS National Map is currently in development.

Example data are available via:

- `data(lake)`

##Installation
This package is not yet on CRAN.  To install

```{r,eval=FALSE}
install.packages("devtools")
library("devtools")
install_github("jhollist/quickmapr")
library("quickmapr")
```

##Using Quickmapr (work in progress)
Basic usage of `quickmapr` is built around a `qmap` object which is simply a list of `sp` or `raster` objects and a recorded plot.  Most of the other `quickmpar` functions will work with a `qmap` object.

To create a qmap object:

```{r}
#First some data
data(lake)
#Create your first quick map and object
qm <- qmap(elev,samples,buffer,width)
```

There are some other options on `qmap` that let you change the draw order, coloring of vectors, extent of the map, and whether or not to preform a basic projection check (data are assumed to be in the same coordinate reference system).

So for instance, if you want to zoom in to the extent of one of your layers you could do something like:

```{r}
#Zoom to the extent of the layer named width
qm<-qmap(elev,samples,buffer,extent=width)
```

Currently this is only working with object in memory and not pulling from the `qmap` object.  

You can change colors (this is still a bit clunky).

```{r}
#draw samples and width in red and buffer with blue fill
qm<-qmap(elev,samples,buffer,order = c(2,1,3), colors = c("red","red","blue"), fill=TRUE)
```

Basemaps can be added from the USGS' National Map (still VERY experimental and slow)

```{r}
#Get The Basemap
basem <- get_basemap(qm$map_extent,proj4string(qm$map_data[[1]]),width=1000)
qm <- qmap(qm,basemap = basem)
```

Zooming and panning are accomplished with zi(),ze(),zo(),f(), and p():

```{r, eval=FALSE}
#Zoom in on selected point
zi(qm)
#Zoom in on a chosen extent
ze(qm)
#Zoom out form selected point
zo(qm)
#Go out to full extent
f(qm)
#pan
p(qm)
```
