% !TeX root = RJwrapper.tex
\title{\texttt{quickmapr}: Simplified mapping and basic interactivity.}
\author{by Jeffrey W. Hollister}

\maketitle

\abstract{%
There are many packages that already exist or are in active development
that support the visualization of spatial data in R. However, there
seems to be a gap for those that need to quickly view, compare, and
interactively explore the results of a given spatial analysis without
first having to convert to a different coordinate reference system.
Functionality for the current release (v0.2.0) simplifies mapping of
multiple \texttt{sf}, \texttt{sp} or \texttt{raster} layers, and also
provides interactive zooming, panning, labelling, selecting, and
identifying. These tools are intended for use within an active spatial
analysis workflow and not for production quality maps. Additionally,
\texttt{quickmapr} does not make any assumptions about coordinate
reference systems and leaves managing of projections to the analyst.
This paper introduces the package and shows examples of its typical use.
}

\subsection{Introduction}\label{introduction}

Spatial data analysis capabilities in R have been steadily growing over
the last several years. We are now to the point where nearly all
Geographic Information Systems (GIS) functionality can be accomplished
without leaving R. The one area that had lagged behind was spatial data
visualization and interactivity. This too is changing rapidly.
Initially, spatial data visualization had been handled via base plotting
methods (e.g from \CRANpkg{sp} or \CRANpkg{raster}) or via additional
plotting packages such as
\CRANpkg{ggplot2}\citep{pebesma2005classes, bivand2013asdar, raster, ggplot2}.
While these methods provide the ability to make high quality maps, they
do not provide interactivity, a hallmark of GIS.

To address this, most solutions (e.g. \CRANpkg{ggmap},
\CRANpkg{leaflet}, \CRANpkg{mapview} etc.) have relied on javascript
libraries or other web APIs \citep{ggmap, leaflet, mapview}. These
provide a modern interface, with a rich set of basemaps, but all assume
a geographic coordinate system or Web Mercator coordinate reference
system. In the case of typical spatial data analysis workflow it is
often desirable to quickly map the resultant spatial datasets in the
projection chosen for the analysis. Currently, this is not possible with
the most used javascript libraries. I developed \CRANpkg{quickmapr} to
fill this gap and provide spatial data analysts with a tool to quickly
map multiple layers and interact with the resultant map without having
to utilize various APIs or external libraries and without having to
re-project data.

The goals of this paper are to describe the basic usage of
\pkg{quickmapr}, show several examples of its use, and outline changes
expected in future versions. We also briefly discuss the contribtuion
that \pkg{quickmapr} makes to the existing suite of spatial data
visualization tools in R.

\subsection{Basic usage}\label{basic-usage}

\subsection{The \code{qmap} function and
object}\label{the-function-and-object}

\subsection{Zooming and panning}\label{zooming-and-panning}

\subsection{Identification and
selection}\label{identification-and-selection}

\subsection{Basemaps from the USGS National
Map}\label{basemaps-from-the-usgs-national-map}

\subsection{Summary}\label{summary}

This file is only a basic article template. For full details of
\emph{The R Journal} style and information on how to prepare your
article for submission, see the
\href{https://journal.r-project.org/share/author-guide.pdf}{Instructions
for Authors}.

\bibliography{hollister}

\address{%
Jeffrey W. Hollister\\
U.S. Environmental Protection Agency\\
Office of Research and Development\\ National Health and Environmental Effects Research Laboratory\\ Atlantic Ecology Division\\ 27 Tarzwell Drive\\ Narragansett, RI 02882\\
}
\href{mailto:hollister.jeff@epa.gov}{\nolinkurl{hollister.jeff@epa.gov}}

